---
title: "Tutorial: Advanced data visualization in R"
subtitle: "70th Biometrical Colloquium 2024 in Luebeck"
---

This is the supporting material for the tutorial **Advanced data visualization in R** which takes place on the 28.02.2024 09:00-12:00. Here is the tutorial description as displayed on the [website's conference program](https://www.biometrische-gesellschaft.de/en/events/biometric-colloquia/70th-biometrical-colloquium-2024-in-luebeck/conference-program.html):

> **Advanced data visualization in R: (Re)producing professional plots with ggplot2 and the tidyverse**
>
> Lecturer: Paul Schmidt (BioMath GmbH, Hamburg)
> 
> Learning objectives:
> 
> - Deep dive into ggplot2: Understand the intricacies of ggplot2 for top-tier data visualization
> - Data manipulation with tidyverse: Utilize packages like dplyr, tidyr, and forcats to shape data optimally for creating graphs
> - Aestetic fine-tuning: Master the skills of axis formatting, theme detailing, and color selection
> - Reproducing Exercise: Recreate published plots to understand the application of ggplot2 techniques in real-world scenarios
> - Exporting excellence: Learn best practices for exporting plots in publication-ready formats
> 
> Target group:
> 
> - Anyone wanting to produce or present high-quality plots. Conveying complex data insights through refinde visualizations is a relevant part of statistical analysis
> 
> Prerequisites:
> 
> - Basic understanding of R programming is required
> - Basci knowledge of ggplot2 and the tidyverse is beneficial, but not required
> - R-packages: tidyverse, cowplot, ggrepel, ggtext, viridis
> 
> Format: Hybrid

```{r, include=FALSE, warning=FALSE, message=FALSE}

```

# Part 0: Setup

You will need to install the following packages

```{r, eval=FALSE}
install.packages("cowplot")
install.packages("gapminder")
install.packages("ggrepel")
install.packages("ggtext")
install.packages("tidyverse")
install.packages("virids")
```

# Part 1: A single plot

# Part 2: Multiple plots
